Reasoning About a Machine with Local Capabilities

### 2018-05-16 toplas/paper.tex
Made a tikz figure to replace the the world/capability picture

\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{multirow,bigdelim}

@@

Interestingly, this idea is a variant of a notion of public/private future
worlds that has been previously used in the literature (see
\sectionname~\ref{sec:discussion}). However, temporary regions are new in our setting
and there is an interesting interplay with the recursiveness of the worlds: for
a temporary region, the predicate $H \in \Worlds \rightarrow
\powerset{\MemSegments}$ (which defines the safe memory segments in the
current world) is only required to be monotone w.r.t.\ public
future worlds (i.e.\ safe memory segments remain safe in public future worlds),
but for permanent regions, it must be monotone w.r.t.\ private future worlds.
As a consequence, the memory for a permanent region may not contain local
capabilities (as their safety would be broken in private future worlds), which
in turn implies that only local capabilities may have write-local permission (a
general sanity requirement when using local capabilities\footnote{In fact, local
  capabilities become useless as soon as the adversary has access to a single
  global, write-local capability.})\footnote{For explanation purposes, this
  discussion ignores certain ways to allow for local capabilities in a permanent
  region, for example, by not requiring that they are valid or requiring that
  they are local versions of valid global capabilities.}.
\end{toplas}
\subsection{Worlds}
\label{subsec:worlds}
\begin{figure}[htb]
  \centering
  \includegraphics{w11}

>>>>

\usepackage{tikz}
\usetikzlibrary{positioning,patterns,arrows,automata,decorations.markings}
\usepackage{multirow,bigdelim}

@@

Interestingly, this idea is a variant of a notion of public/private future
worlds that has been previously used in the literature (see
\sectionname~\ref{sec:discussion}). However, temporary regions are new in our setting
and there is an interesting interplay with the recursiveness of the worlds: for
a temporary region, the predicate $H \in \Worlds \rightarrow
\powerset{\MemSegments}$ (which defines the safe memory segments in the
current world) is only required to be monotone w.r.t.\ public
future worlds (i.e.\ safe memory segments remain safe in public future worlds),
but for permanent regions, it must be monotone w.r.t.\ private future worlds.
As a consequence, the memory for a permanent region may not contain local
capabilities (as their safety would be broken in private future worlds), which
in turn implies that only local capabilities may have write-local permission (a
general sanity requirement when using local capabilities\footnote{In fact, local
  capabilities become useless as soon as the adversary has access to a single
  global, write-local capability.})\footnote{For explanation purposes, this
  discussion ignores certain ways to allow for local capabilities in a permanent
  region, for example, by not requiring that they are valid or requiring that
  they are local versions of valid global capabilities.}.
\end{toplas}
\subsection{Worlds}
\label{subsec:worlds}
\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    \scope
    \clip (-.1,-.1) rectangle (4.6,11.1);
    \fill[fill=white] (0,0) rectangle (4.5,11);
    \draw (0,0) -- (0,11);
    \draw (4.5,0) -- (4.5,11);
    \endscope
    % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);
    \draw (-1.5,0) node {};
    \draw (-1.5,15) node {};

    \foreach \x in {0.5,1,...,4.5}
    {
      \shade[left color=blue!70,right color=white] (0,\x) rectangle (4.5,\x+.5);
      \draw (0,\x) rectangle (4.5,\x+.5);
    };
    \foreach \x in {5,5.5,...,7}
    {
      \fill[color=red!55] (0,\x) rectangle (4.5,\x+.5);
      \draw (0,\x) rectangle (4.5,\x+.5);
    };
    \foreach \x in {7.5,8,...,10}
    {
      \fill[color=green!85] (0,\x) rectangle (4.5,\x+.5);
      \draw (0,\x) rectangle (4.5,\x+.5);
    };

    \draw [decorate,decoration={brace,amplitude=5pt,mirror,raise=0pt},yshift=0pt]
    (4.6,1.5) -- (4.6,3) node (a) [black,midway] {};
    \draw [decorate,decoration={brace,amplitude=5pt,raise=0pt,aspect=0.3},yshift=0pt]
    (-0.1,0.5) -- (-0.1,3) node (b) [black,midway,xshift=0.8cm] {};
    \draw [decorate,decoration={brace,amplitude=5pt,raise=0pt},yshift=0pt]
    (-0.1,3) -- (-0.1,4.5) node (c) [black,midway,xshift=0.8cm] {};
    \draw [decorate,decoration={brace,amplitude=5pt,raise=0pt},yshift=0pt]
    (-0.1,5) -- (-0.1,7) node (d) [black,midway,xshift=0.8cm] {};
    \draw [decorate,decoration={brace,amplitude=5pt,raise=0pt,aspect=0.6},yshift=0pt]
    (-0.1,7.5) -- (-0.1,10.5) node (e) [black,midway,xshift=0.8cm] {};

    \tikzset{capa/.style={decoration={markings,mark=at position 0 with %
    {\fill[black] circle(1.5pt);}}}}

    \draw[capa] (-4,8.5) edge[-latex,postaction={decorate},in=180,out=30,densely dashed] (-0.4,9.3);

    \draw[capa] (-4,6.8) edge[-latex,postaction={decorate},in=180,out=-30] (-0.4,6);
    \draw[capa] (-4,4.55) edge[-latex,postaction={decorate},in=180,out=-30] (-0.4,3.75);

    \draw[capa] (-4,2.05) edge[-latex,postaction={decorate},in=180,out=-30,densely dashed] (-0.4,1.25);

    \draw[capa] (4.25,6.25) edge[-latex,postaction={decorate},in=0,out=0] (4.9,2.25);

    \draw (-2,4.25) edge[color=red,thick] (-1,3.25)
          (-1,4.25) edge[color=red,thick] (-2,3.25);
    \draw (5.35,3.85) edge[color=red,thick] (6.35,2.85)
          (6.35,3.85) edge[color=red,thick] (5.35,2.85);

    \node at (-8,10) (perm) {\footnotesize Permanent region};
    \node at (-8,9) (temp) {\footnotesize Temporary region};
    \node at (-8,8) (temp) {\footnotesize Local capability};
    \node at (-8,7) (temp) {\footnotesize Global capability};

    \fill[color=green!85] (-12.5,9.75) rectangle (-11.5,10.25);
    \fill[color=red!55] (-11.5,9.75) rectangle (-10.5,10.25);
    \fill[color=green!85] (-11.75,9.75) -- (-11.75,10.25) -- (-11.25,10.25);    
    \fill[color=red!55] (-11.75,9.75) -- (-11.25,9.75) -- (-11.25,10.25);
    \draw (-12.5,9.75) rectangle (-10.5,10.25);

    \shade[left color=blue!70,right color=white] (-12.5,8.75) rectangle (-11.5,9.25);
    \draw (-12.5,8.75) rectangle (-10.5,9.25);

    \draw[capa] (-12.4,8) edge[-latex,postaction={decorate},in=180,out=30,densely dashed] (-10.5,8);
    \draw[capa] (-12.4,7) edge[-latex,postaction={decorate},in=180,out=30] (-10.5,7);
    \draw (-13,10.6) rectangle (-5.4,6.4);
  \end{tikzpicture}
